---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fqadata

<!-- badges: start -->
[![R-CMD-check](https://github.com/ifoxfoot/fqadata/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ifoxfoot/fqadata/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

`fqadata` contains regional Floristic Quality Assessment  databases that have been approved or approved with reservations by the U.S. Army Corps of Engineers. Paired with the [fqacalc](https://github.com/ifoxfoot/fqacalc) package, these datasets allow for Floristic Quality Assessment metrics to be calculated. Both packages were developed for the USACE by the U.S. Army Engineer Research and Development Center's Environmental Laboratory.

## Installation

You can install the development version of fqadata from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ifoxfoot/fqadata")
```

## Example

To access the data:

```{r example}
library(fqadata)

#view data set
head(fqa_db)
```

